Resilience and Home-Space for WSTS \thanks{This work was partly done while the authors were supported by the Agence Nationale de la Recherche grant BraVAS (ANR-17-CE40-0028).}

### 2023-08-31 final.tex
up

We now consider the case $\Safe = \downarrow \Safe$.
%
Unfortunately the {\sc State-resilience} problem is undecidable in this case. As for resilience in WSTS when $\Safe = \downarrow \Safe$, it stems from undeciability of the corresponding problem in Minsky machines, the executions of which can be simulated by reset-VASS, as seen in 
Section~\ref{safe-down}.

>>>>

We now consider the case $\Safe = \downarrow \Safe$.
%
Unfortunately {\sc State-resilience} is undecidable in this case. As for {\sc Resilience} in WSTS when $\Safe = \downarrow \Safe$, this stems from undeciability of the corresponding problem in Minsky machines, the executions of which can be simulated by reset-VASS, as seen in 
Section~\ref{safe-down}.
